---
title: "Social Survey"
author: "Put your name here!"
date: "put the date here"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS2016_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   

####This study deals with questions about possible relationships between views toward extramrital sex and sex, political views, and current relationship status. The data is from the 2016 general social survey.



# Sex

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Polyviews

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
polyxmar <- xtabs(~POLVIEWS+XMARSEX,data=shortDat)
polyxmar
```

```{r}
barchartGC(polyxmar,type="percent")
```

At first glance, the barcharts look to be expected. the majority say extra marrigal sex is wrong and few say its ok, but upon further review, the liberal and conservative barcharts vary alot. 95% of conservatives said extra marrigal sex is wrong while only 80% of liberals said its wrong with moderate being somewhere in between. Looking at the chart above from left to right, the "wrong" bar gets bigger while the "hmm"" and "ok"" bars shrink. the relation is pretty clear and i predict a high p value to come out of the ttest.  

```{r}
t.test(polyxmar)
```

contrary to my prediction, the pvalue came out to 0.05 which is the division where statisticians consider where to reject the null hypothesis or not. according to that logic, these peoples political views have no relation to wheather they think extra marrigal sex is ok or wrong, but after looking at the numbers, i disagree. i believe there is a relation and maybe i just did something wrong with the ttest.

#Relationship Status



# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
