---
title: "Social Survey"
author: "Put your name here!"
date: "put the date here"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS2016_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   

####This study deals with questions about possible relationships between views toward extramrital sex and sex, political views, and current relationship status. The data is from the 2016 general social survey.



# Sex

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
xmarsexandsex <- xtabs(~SEX+XMARSEX,data=shortDat)
xmarsexandsex
```
  
thanks to the table above, we can see that thhere are about 200 more females than males and even so, more males voted hmm an ok than females did
```{r}
barchartGC(xmarsexandsex,type="percent")
```
  
At first glance, both barcharts look identical and upon further glance, they are both very similar. As expected the large majority of subjects in both groups said extra marrige sex is wrong but there is a slight difference in that a fewer percent of males than females said it was wrong.

```{r}
t.test(xmarsexandsex)
```
  
The p-value is 0.12 which is higher than 0.05. this means that there is some relation and not just at random.

# Polyviews

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
polyxmar <- xtabs(~POLVIEWS+XMARSEX,data=shortDat)
polyxmar
```

```{r}
barchartGC(polyxmar,type="percent")
```

At first glance, the barcharts look to be expected. the majority say extra marrigal sex is wrong and few say its ok, but upon further review, the liberal and conservative barcharts vary alot. 95% of conservatives said extra marrigal sex is wrong while only 80% of liberals said its wrong with moderate being somewhere in between. Looking at the chart above from left to right, the "wrong" bar gets bigger while the "hmm"" and "ok"" bars shrink. the relation is pretty clear and i predict a high p value to come out of the ttest.  

```{r}
t.test(polyxmar)
```

contrary to my prediction, the pvalue came out to 0.05 which is the division where statisticians consider where to reject the null hypothesis or not. according to that logic, these peoples political views have no relation to wheather they think extra marrigal sex is ok or wrong, but after looking at the numbers, i disagree. i believe there is a relation and maybe i just did something wrong with the ttest.

#Relationship Status

```{r}
singles <- filter(shortDat, RELATSEX=="Single")
tblatxmars <- table(singles$XMARSEX)
barchartGC(tblatxmars,type="percent", main="Extra marital sex single")
```
```{r}
hookeds <- filter(shortDat, RELATSEX=="Hooked UP")
tblatxmarh <- table(hookeds$XMARSEX)
barchartGC(tblatxmarh,type="percent", main="Extra marital sex hooked up")
```

Just by looking at the barcharts above, you can see that for both relationship statuses, most would say it is wrong, but the percent of single people that said it is ok, is larger than the percent of hooked up people that said it is ok. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

we conclude that the data in some way is related to eachother. for example, we found out that a male was more likely to say extramarrigal sex was ok than a female was meaning a woman might value a relationship more than a male would. the biggest relations came with the political views. I have no knowledge in politics and dont know what a liberal or conservative is, but it seems liberals are a little more loose when it comes to relationships than conservatives who are very strict. when it comes to your curent relationship status, the reults are to be expected. single people are more likely to say extra marrigal sex is ok than a person who is currently in a relationship. My guess is that someone who is currently single doesnt value loyalty as much as someone who has a partner or spouse. i have gathered that your gender, political views, and your current relationship status all influence your opinion on extra marrigal sex.