---
title: "Social Survey"
author: "Put your name here!"
date: "put the date here"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS2016_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   

####This study deals with questions about possible relationships between views toward extramrital sex and sex, political views, and current relationship status. The data is from the 2016 general social survey.



# Sex

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Polyviews

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

# Relationship Status

```{r}
singles <- filter(shortDat, RELATSEX=="Single")
tblatxmars <- table(singles$XMARSEX)
barchartGC(tblatxmars,type="percent", main="Extra marital sex single")
```
```{r}
hookeds <- filter(shortDat, RELATSEX=="Hooked UP")
tblatxmarh <- table(hookeds$XMARSEX)
barchartGC(tblatxmarh,type="percent", main="Extra marital sex hooked up")
```

Just by looking at the barcharts above, you can see that for both relationship statuses, most would say it is wrong, but the percent of single people that said it is ok, is larger than the percent of hooked up people that said it is ok. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
